Supplement A: Community Clustering

### 2024-02-16 R/community-clustering.qmd
update description of algorithm and replace depracated igraph function

Here the population, $N$, of focal center $c$ is defined as

$$N_{c} = R_{c} + \sum_{k=1}^{S} R_{k} \cdot I(t_{kc} \leq D_{c})$$

for all sites $S$ (this includes both farms and centers), with $R_{c}$ being the
room count at $c$ and $R_{k}$ the room count at site $k$, $t_{kc}$ the travel
time from $k$ to $c$, $D_{c}$ the threshold travel time to $c$ (referred to as
*D-join* in the paper), and $I$ the indicator function that is 1 if $t \leq D$
and 0 otherwise.

@@

  # there's a recursive dimension to this:
  # if a center is joined with a center that's joined with a center, etc.
  # i don't know how to do that in R
  # so, igraph it is...
  g <- igraph::graph.adjacency(neighbors_matrix)
  membership <- igraph::components(g)[["membership"]]

@@

ggsave(
  plot = gg,
  filename = fn,
  width = 6.6,
  height = 7.33,
  dpi = 600
)

>>>>

Here the catchment room count, $N$, of focal center $c$ is defined as

$$N_{c} = \sum_{k=1}^{S} R_{k} \cdot I(t_{kc} \leq D)$$

for all sites $S$ (including both farms and centers), with $R_{k}$ being the
room count at site $k$, $t_{kc}$ the travel time from $k$ to $c$, $D$ the
threshold travel time to a center (referred to as *D-join* in the paper), and
$I$ the indicator function that is 1 if $t \leq D$ and 0 otherwise. Note that
$S$ includes $c$ and that $t_{cc} = 0$ (the travel time from a center to the
same center is precisely 0), so $R_{c}$ is always included in $N_{c}$.

The catchment room count within $D$ of two centers $c$ and $d$ is then

$$N_{cd} = \sum_{k=1}^{S} R_{k} \cdot I(t_{kc} \leq D) \cdot I(t_{kd} \leq D)$$

and

$$p_{cd} = N_{cd}/N_{c}$$

so we could also state our rule as: if $p_{cd} \geq \alpha$ for some critical
threshold $\alpha$, then $c$ is part of the same community as $d$. In this case,
the default threshold is 0.8 relative to a commute time distance of one half
hour.

@@

  # there's a recursive dimension to this:
  # if a center is joined with a center that's joined with a center, etc.
  # i don't know how to do that in R
  # so, igraph it is...
  g <- igraph::graph_from_adjacency_matrix(neighbors_matrix)
  membership <- igraph::components(g)[["membership"]]

@@

ggsave(
  plot = gg,
  filename = fn,
  width = 6.7,
  height = 7.,
  dpi = 600
)
